Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media

### 2015-11-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Update Manuscript_ViscousInstabilities_KC.tex

\begin{abstract}

Accurate simulation of multiphase flows in porous media remains a challenge \red{(Why? Sentencing is hanging ... word `accurate' is vague here! The second sentence is not gramatically correct and too simplistic -- see notes below.)}. While the governing equations are the conservation of mass and Darcy's law, there are also the primary variables, such us pressure, velocity, saturation and permeability. This paper introduces a multi-fluid porous media flow model which is the basis of a reservoir simulator, as implemented in Fluidity, a general purpose flow simulator that is equipped with anisotropic mesh adaptivity techniques to control the local solution errors and  increase the computational accuracy in the research on the development of numerical methods in geophysical fluid mechanics. The governing multiphase porous media flow equations are solved using the adaptive and unstructured mesh.
The model is based upon two key numerical characteristics: (a) the family of $P_{n}DG-P_{n+1}$ finite element pairs and (b) a consistent overlapping control volume finite element method (CVFEM) formulation.
%The element type described above has a discontinuous $n^{th}$ order polynomial representation of velocity and a continuous $(n+1)^{th}$ representation for pressure. This method includes the Darcy force balance equation, pressure, velocity and saturation fields throughout the domain while there is automatic mesh adaptivity in space and time and the computational cost is reduced.} 
Numerical modelling of multiphase flows in porous media has application in a wide range of disciplines, from hydrocarbons exploration and extraction to groundwater operations.Viscous fingering, member of the flow instabilities family, is a major concern for the oil \& gas industry, but not only to this. The impact of fingers formation in our simulations is also investigated.  
%This paper describes a  In particular, the \PNDG[1]{1} element (i.e., discontinuous and piecewise linear shape functions to discretise velocity and pressure fields) is introduced as the basis of the discretisation and also as the CVFEM counterpart. In addition to the unstructured grid used for the simulations, uniform and random permeability distribution are introduced. The formulation is applied to saturated porous media systems.
We conclude that understanding the multiphase flow properties will allow us to efficiently facilitate more efficient oil \& gas recovery, efficient contaminant removal and better planning of carbon capture and storage projects.

>>>>

\begin{abstract} 
Numerical modelling of multiphase flow in porous media has applications in a wide range of disciplines Accurate prediction of multiphase flows in porous media remains one of the problems. While the governing equations are the conservation of mass and Darcy's law, there are also the primary variables, such us pressure, velocity, saturation and permeability. This paper introduces a multi-fluid porous media flow model which is the basis of a general purpose flow simulator that is equipped with anisotropic mesh adaptivity techniques to control the local solution errors and  increase the computational accuracy in the research on the development of numerical methods in geophysical fluid mechanics. The governing multiphase porous media flow equations are solved using the adaptive and unstructured mesh.
The model is based upon two key numerical characteristics: (a) the family of $P_{n}DG-P_{n+1}$ finite element pairs and (b) a consistent overlapping control volume finite element method (CVFEM) formulation.
%The element type described above has a discontinuous $n^{th}$ order polynomial representation of velocity and a continuous $(n+1)^{th}$ representation for pressure. This method includes the Darcy force balance equation, pressure, velocity and saturation fields throughout the domain while there is automatic mesh adaptivity in space and time and the computational cost is reduced.} 
Numerical modelling of multiphase flows in porous media has application in a wide range of disciplines, from hydrocarbons exploration and extraction to groundwater operations.Viscous fingering, member of the flow instabilities family, is a major concern for the oil \& gas industry, but not only to this. The impact of fingers formation in our simulations is also investigated.  
%This paper describes a  In particular, the \PNDG[1]{1} element (i.e., discontinuous and piecewise linear shape functions to discretise velocity and pressure fields) is introduced as the basis of the discretisation and also as the CVFEM counterpart. In addition to the unstructured grid used for the simulations, uniform and random permeability distribution are introduced. The formulation is applied to saturated porous media systems.
We conclude that understanding the multiphase flow properties will allow us to efficiently facilitate more efficient oil \& gas recovery, efficient contaminant removal and better planning of carbon capture and storage projects.
